---
title: "AdvStas_HW4"
author: "Paridhi Agal"
date: "2/19/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("forecast")
library("tseries") 

```

# 1. Step-by-Step fit different ARIMA (p,d,q) x (P, D, Q) for FAANG stock price series. Can you discover a better model than auto.arima?

# 2. Select the best model using information criteria (AIC, AICC, BIC), and present out-of-sample forecasts with prediction intervals

# 3. Discover a set of good models. Try combining forecasts from a few good models. 




```{r}
setwd("F:/UCD Business Analytics/2 Winter Quarter/442 Advance Stats/Homework 4/HW4 Data")
apple<-read.csv("aapl.csv", sep=",",dec=".",header=T) 	# daily data
names(apple)
head(apple,5)
amazon<-read.csv("amzn.csv", sep=",",dec=".",header=T) 	# daily data
names(amazon)
head(amazon,5)
fb<-read.csv("FB.csv", sep=",",dec=".",header=T) 	# daily data
names(fb)
head(fb,5)
google<-read.csv("goog.csv", sep=",",dec=".",header=T) 	# daily data
names(google)
tail(google,5)
netflix<-read.csv("nflx.csv", sep=",",dec=".",header=T) 	# daily data
names(netflix)
tail(netflix,5)
```

```{r}
#apple[,1]
str(apple)

```


```{r}
yy_t = cbind(apple[,1],apple[,5], amazon[,5],fb[,5],google[,5],netflix[,5])
head(yy_t)

```



```{r}
inds= seq(as.Date("2019-02-11"),as.Date("2020-02-07"), by="day")
set.seed(50)
yy_apple = ts(apple[,5], frequency = 365,start = c(2019,as.numeric(format(inds[1],"%j"))))		# coverts sales data as time series object with start date and frequency (daily here)
plot.ts(yy_apple)	
yy_amazon = ts(amazon[,5], frequency = 365,start = c(2019,as.numeric(format(inds[1],"%j"))))		# coverts sales data as time series object with start date and frequency (daily here)
plot.ts(yy_amazon)	
yy_fb = ts(fb[,5], frequency = 365,start = c(2019,as.numeric(format(inds[1],"%j"))))		# coverts sales data as time series object with start date and frequency (daily here)
plot.ts(yy_fb)	
yy_google = ts(google[,5], frequency = 365,start = c(2019,as.numeric(format(inds[1],"%j"))))		# coverts sales data as time series object with start date and frequency (daily here)
plot.ts(yy_google)	
yy_netflix = ts(netflix[,5], frequency = 365,start = c(2019,as.numeric(format(inds[1],"%j"))))		# coverts sales data as time series object with start date and frequency (daily here)
plot.ts(yy_netflix)	
```




```{r}
yy = cbind(yy_apple, yy_amazon,yy_fb,yy_google,yy_netflix)
head(yy)

```

```{r}
yd= data.frame(matrix(0, nrow=250, ncol= 5))
colnames(yd) = c("apple", "amazon", "fb", "google","netflix")
for (i in seq(1,5,1)){
  adf.test(yy[,i])
  yd[,i] = diff(yy[,i],differences = 1)			
  plot.ts(yd[,i])	# looks stationary visually but test it
  adf.test(yd[,i])
  #x['p.value']
}

```

```{r}
#for q
for (i in seq(1,5,1)){
  Acf(yd[,i], lag.max = 10, main= colnames(yd)[i])
}

# q for ma is 1 for all
```



```{r}
# adf.test(yd[,5])
# for p
for (i in seq(1,5,1)){
  Pacf(yd[,i], lag.max = 10, main= colnames(yd)[i])
}

# p for AR is 0 for all
```

p = non-seasonal AR order, d = non-seasonal differencing, q = non-seasonal MA order, P = seasonal AR order, D = seasonal differencing, Q = seasonal MA order, and S = time span of repeating seasonal pattern


```{r}


```

## 
```{r}
m1_apple = Arima(yy_apple, order=c(2,1,2), seasonal= list(order= c(0,1,1), period= 60))
m1_apple


```

```{r}
m2_amazon = Arima(yy[,2], order=c(1,1,0), seasonal= list(order= c(0,1,1), period= 120))
m2_amazon


```

```{r}
m3_fb = Arima(yy[,3], order=c(0,1,0), seasonal= list(order= c(0,1,1), period= 60))
m3_fb


```


```{r}
m4_google = Arima(yy[,4], order=c(0,1,0), seasonal= list(order= c(0,1,1), period= 60))
m4_google


```


```{r}
m5_netflix = Arima(yy[,5], order=c(1,1,1), seasonal= list(order= c(0,1,1), period= 60))
m5_netflix


```


```{r}
# auto arima for apple

aa1 = auto.arima(yy[,1])
aa1
```



```{r}
# auto arima for amazon

aa2 = auto.arima(yy[,2])
aa2
```


```{r}
# auto arima for fb

aa3 = auto.arima(yy[,3])
aa3
```

```{r}
# auto arima for google

aa4 = auto.arima(yy[,4])
aa4
```


```{r}
google_predict_auto = forecast:::forecast.Arima(aa4, h = 14 , level = c(68, 90) )
#plot(google_predict_auto)
#google_predict_auto
```


```{r}
# auto arima for netflix

aa5 = auto.arima(yy[,5])
aa5
```

Predict for Feb 24 to Feb28th , but Feb 17th was a holiday so predictiing  so 10 to 14 is the level


```{r}

apple_predict = forecast:::forecast.Arima(m1_apple, h = 14 , level = c(68, 90) )
plot(apple_predict)
apple_predict
final = data.frame(matrix(0,nrow=5,ncol=6))
colnames(final)= c("2020-02-21","2020-02-24","2020-02-25","2020-02-26","2020-02-27","2020-02-28")
rownames(final) = c("apple", "amazon", "fb", "google","netflix")
final[1,]= as.numeric(apple_predict$mean)[9:14]
final
#c(302, 306)
```

```{r}

amazon_predict = forecast:::forecast.Arima(m2_amazon, h = 14 , level = c(68, 90) )
plot(amazon_predict)
amazon_predict
final[2,]= as.numeric(amazon_predict$mean)[9:14]
final
#c(302, 306)
```

```{r}

fb_predict = forecast:::forecast.Arima(m3_fb, h = 14 , level = c(68, 90) )
plot(fb_predict)
fb_predict
final[3,]= as.numeric(fb_predict$mean)[9:14]
final
#c(302, 306)
```

```{r}

google_predict = forecast:::forecast.Arima(m4_google, h = 14 , level = c(68, 90) )
plot(google_predict)
google_predict
final[4,]= as.numeric(google_predict$mean)[9:14]
final
#c(302, 306)
```


```{r}

netflix_predict = forecast:::forecast.Arima(m5_netflix, h = 14 , level = c(68, 90) )
plot(netflix_predict)
netflix_predict
final[5,]= as.numeric(netflix_predict$mean)[9:14]
final
#c(302, 306)
```

```{r}
final[1,]= final[1,]-13
final[5,] = final[5,]+c(10,10,10,10,10)

```

```{r}
dplyr::select(final,-1)
```
