---
title: "R Notebook"
output: html_notebook
---
```{r}
# read the data
library(glmnet)
library(MASS)
data= read.csv("F:/UCD Business Analytics/2 Winter Quarter/442 Advance Stats/Class 3/Cars_Data.csv", header=T)
head(data)

```




```{r}
cor_data=as.matrix(data[,2:16]) # base data
xcor = cor(as.matrix(cor_data)) #correlation
#pairs(xcor)

```

```{r}
# Eigen decomposition 
out = eigen(xcor)  # eigen decomposition of correlation matrix. Yields eiganvalues and eigenvectors

va = out$values		# eigenvalues
ve = out$vectors	# eigenvectors. Each column is an eigenvector and has a unit length. 	
va
ve

perc_data_explained = as.integer(va/sum(va)*100)
perc_data_explained
```

```{r}
# Scree Plot		# to decide how many variables to keep. Look for "elbow" in the scree plot
plot(va, type = "o", col = "blue")


# in the scree plot we can see two elbows 
# one elbow at 1 and other at 3

# as per question we have to take 2 
```


```{r}

# eigenvector proivdes the weights to create new variables (aka loadings)

w1 = ve[,1]			
w2 = ve[,2]	

value = w1[1]

max_value_index <- function(input_vector) {
  max_value = max(input_vector)
  col_names = colnames(cor_data)
  variable = col_names[which(input_vector %in% max_value)]
  return(variable)
}

max_value_index(w2)
max_w1 = max(w1)
which(w1 %in% max_w1)
col_names = colnames(cor_data)
col_names[which(w1 %in% max_w1)]


# check each eignvector has unit length (for your learning)
chk = t(w1) %*% w1

names(w1) = col_names
names(w2) = col_names




-w1[(w1>0.3) | w1<(-0.3)] # gives the variables contributing towards the principal component

#  Attractive        Quiet Poorly.Built     Prestige   Successful 
#  -0.3262814   -0.3173818    0.3319244   -0.3322855   -0.3155394
-w2[(w2>0.3) | w2<(-0.3)] # gives the variables contributing towards the principal component

# Unreliable       Sporty        Roomy Easy.Service 
#  -0.4011014    0.4288285   -0.3789204    0.4279673 


# new variables (aka principal components scores) # APQ we have to take only 2 
z1 = cor_data %*% w1
z2 = cor_data %*% w2

z1 = z1*(-1)
z2 = z2*(-1)



z = cbind(z1,z2)
rownames(z) = c('Infinity','Ford','Audi','Toyota','Eagle','Honda','Saab','Pontiac','BMW','Mercury')

zcor = cor(z)
plot(z[,1],z[,2])
plot(z)
text(z,labels=rownames(z),data=z,font=2)

z

row.names(z)<-data[,1]
#colnames(z)<-c("Vector_1","Vector_2")

plot_data = as.data.frame(z)

write.table(z,"plot_data.csv",sep = ",")  

w1
w2
```

```{r}
y=data[,17]                         # dependent variable 
linreg=lm(y~z[,1:2])								# Fit linear regression with those predictors 

# Ideal Vector 										# read my note on Positioning Maps

b1=as.vector(coef(linreg)[2])
b2=as.vector(coef(linreg)[3])

slope.iso.preference = - b1/b2						# Why? Exam Q
paste("slope.iso.preference : ",slope.iso.preference)
slope.ideal.vector = b2/b1 							# Why? Exam Q
paste0("slope.ideal.vector : ",slope.ideal.vector)

angle.iso.preference = atan(slope.iso.preference)*180/pi

paste("angle.iso.preference : ", angle.iso.preference)


angle.ideal.vector = atan(slope.ideal.vector)*180/pi
paste("angle.ideal.vector : ",angle.ideal.vector)
```
```{r}
# pref = 5
abline(a=(5-b0)/b2, b=slope.iso.preference, col=2)
# pref = 6
abline(a=(6-b0)/b2, b=slope.iso.preference, col=2)
text(-2,-3, “pref=5”, cex=0.9, pos=4, col=2)
text(1,-3, “pref=6", cex=0.9, pos=4, col=2)
```


6. Infinity is the focal brand. Recommend what Infinity should do to improve the car’s design
From the brand perceptual map we can see that for Infinity the closest competitor is BMW. To differentiate and improve the car design Infinity needs to become both aspirational (prestigious and better built) and not be perceived as High maintenance (not easy service and unreliable).
We recommend infinity can 
Build infrastructure to give easy and robust after-market service or have tie ups with service centers to help customers rely on the car and the brand.
Infinity can work towards making the car more attractive with the help of advanced designers who can improve the built of the car. Infinity can also work on the messaging of their marketing campaigns to influence customers. This can be done by having popular celebrities in the advertisements who will make the viewers aspire for this car.
 
7. Find the 90% confidence interval for the angle of the ideal vector? Think about how to do it --we will discuss and cover it in the next class.
To calculate the 90% confidence interval for the angle of the ideal vector 
We can take 1000 samples from the data 
For every sample we find the z= f( betas)
Sort z from smallest to largest to give Z
Find the 90% confidence interval by finding [z(50th) , z(950th)] in Z
